---
title: "Shiny_1"
output: html_document
date: "`r Sys.Date()`"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(tidyverse)
```

```{r}
DIG.df <- read_csv("DIG.csv", show_col_types = FALSE)
head(DIG.df)
dig.df <- DIG.df %>% select(ID, TRTMT, AGE, SEX, BMI, KLEVEL, CREAT, DIABP, SYSBP, HYPERTEN, CVD, WHF, DIG, HOSP, HOSPDAYS, DEATH, DEATHDAY)
dig.df <- dig.df %>% mutate(ID = as.factor(ID), 
                            TRTMT = as.factor(TRTMT),
                            AGE = as.numeric(AGE),
                            SEX = as.factor(SEX),
                            BMI = as.numeric(BMI),
                            KLEVEL = as.numeric(KLEVEL),
                            CREAT = as.numeric(CREAT),
                            DIABP = as.numeric(DIABP),
                            SYSBP = as.numeric(SYSBP),
                            HYPERTEN = as.factor(HYPERTEN),
                            CVD = as.factor(CVD),
                            WHF = as.factor(WHF),
                            DIG = as.factor(DIG),
                            HOSP = as.factor(HOSP),
                            HOSPDAYS = as.numeric(HOSPDAYS),
                            DEATH = as.factor(DEATH),
                            DEATHDAY = as.numeric(DEATHDAY)) %>%
  filter(!is.na(HYPERTEN)) %>%
  filter(!is.na(KLEVEL))#filter out na values of hyperten for Q 11
```


```{r eruptions, echo=FALSE}
ui <- fluidPage(
  titlePanel("DIG"),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "Treatment", label = "Select Treatment Type:",
                  choices = c("Placebo", "Treatment"))
    ),
    mainPanel(
      plotOutput("plot1")
    )
  )
)

server <- function(input, output, session) {
  output$plot1 <- renderPlot({
    dig.df %>% filter(TRTMT == input$Treatment) %>%
    ggplot(mapping = aes(x = TRTMT, y = 100*(after_stat(count))
  /sum(after_stat(count)), fill = TRTMT)) + 
  geom_bar(colour = "black",alpha = 0.4) + 
  labs( title = " Barplot of Treatment Type",
        fill = "Treatment vs Placebo",
        x = "Treatment vs Placebo",
        y = "Percentage (%)") + 
  scale_fill_manual(values = c("navyblue", "cyan"))})
  
}

shinyApp(ui, server)
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



